A standard for the scholarly citation of archaeological data as an incentive to data sharing

### 2017-11-29 analysis/paper/paper.Rmd
just need to check the citations and refererences

---
title: "A standard for the scholarly citation of archaeological data as an incentive to data sharing"
author:
  - name          : "Ben Marwick"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Department of Anthropology, University of Washington, Seattle, 98115, WA, USA"
    email         : "bmarwick@uw.edu"
  - name          : "Suzanne E. Pilaar Birch"
    affiliation   : "2"

@@

Data are the building blocks of research, and access to data is necessary to fully understand and extend the work of others (Fienberg et al 1985). Yet archaeological data are often not available for a variety of reasons, including a perceived lack of credit for making data available. The goal of this paper is to present a standard for the scholarly citation of archaeological data, akin to the way we cite publications. The need for this has been motivated by Huggertt’s (2017) findings of low levels of data citation and reuse in archaeology, and Clarke’s (2015) analysis that digital data preservation and management systems are under-developed in archaeology, despite our obligations as stewards of cultural heritage. A standard for data citation is important because it gives credit to the authors or compilers of the data, and so accords them visibility and recognition for their scholarly contribution in a way that is valued broadly in the discipline. A citation standard is also important for tracking the use of the data, and generating metrics about the impact of the dataset on the discipline. Understanding the use of resources such as datasets is important for allocating resources within archaeology and identifying novel research directions.

@@

# What are data?

@@

# What are the ethics of data sharing?

@@

# What are the benefits of data sharing to the individual researcher?

@@

# What do researchers think about sharing data?

@@

# What are the current norms of data sharing?

@@

# Do archaeologists share data?

@@

## Reproducibility and open source materials for this study

@@

## Email requests for data in a published article

@@

## Survey of articles published in the _Journal of Archaeological Science_

@@

## Data sets in repositories tracked by DataCite

@@

# How to share archaeological data?

@@

# How to cite archaeological data?

@@

“The data underpinning the analysis reported in this paper were deposited in the Open Science Framework Repository at http://dx.doi.org/10.17605/OSF.IO/32A87 (Marwick 2017).

>>>>

---
title: "A standard for the scholarly citation of archaeological data as an incentive to data sharing"
author:
  - name          : "Ben Marwick"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Department of Anthropology, University of Washington, Seattle, 98115, WA, USA University of Wollongong, New South Wales, Australia"
    email         : "bmarwick@uw.edu"
  - name          : "Suzanne E. Pilaar Birch"
    affiliation   : "2"

@@

Data are the building blocks of research, and access to data is necessary to fully understand and extend the work of others (Fienberg et al 1985). Yet archaeological data are often not available for a variety of reasons, including a perceived lack of credit for making data available. The goal of this paper is to present a standard for the scholarly citation of archaeological data, akin to the way we cite publications. The need for this has been motivated by Huggett’s (2017) findings of low levels of data citation and reuse in archaeology, and Clarke’s (2015) analysis that digital data preservation and management systems are under-developed in archaeology, despite our obligations as stewards of cultural heritage. A standard for data citation is important because it gives credit to the authors or compilers of the data, and so accords them visibility and recognition for their scholarly contribution in a way that is valued broadly in the discipline. A citation standard is also important for tracking the use of the data, and generating metrics about the impact of the dataset on the discipline. Understanding the use of resources such as datasets is important for allocating resources within archaeology and identifying novel research directions.

@@

# What are Data?

@@

# What are the Ethics of Data Sharing?

@@

# What are the Benefits of Data Sharing to the Individual Researcher?

@@

# What do Researchers Think about Sharing Data?

@@

# What are the Current Norms of Data Sharing?

@@

# Do Archaeologists Share Data?

@@

## Reproducibility and Open Source Materials for this Study

@@

## Email Requests for Data in a Published Article

@@

## Survey of Articles Published in the _Journal of Archaeological Science_

@@

## Datasets in Repositories Tracked by DataCite

@@

# How to Share Archaeological Data?

@@

# How to Cite Archaeological Data?

@@

“The data underpinning the analysis reported in this paper were deposited in the Open Science Framework Repository at http://doi.org/10.17605/OSF.IO/32A87 (Marwick 2017).
